---
title: "Developer Meeting: Workshop"
output:
  BiocStyle::html_document:
    toc: false
vignette: >
  % \VignetteIndexEntry{Developer Meeting: Workshop}
  % \VignetteEngine{knitr::rmarkdown}
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
options(width=100, max.print=1000)
knitr::opts_chunk$set(
    eval=as.logical(Sys.getenv("KNITR_EVAL", "TRUE")),
    cache=as.logical(Sys.getenv("KNITR_CACHE", "TRUE")))
```

Author: Martin Morgan (<a
  href="mailto:mtmorgan@fredhutch.org">mtmorgan@fredhutch.org</a>)<br/ >
Date: 7 September, 2015<br />

The material in this document requires _R_ version 3.2 and
_Bioconductor_ version 3.2

```{r configure-test}
stopifnot(
    getRversion() >= '3.2' && getRversion() < '3.3',
    BiocInstaller::biocVersion() == "3.2"
)
```

# Content

- W0. [Overview](W0-Overview.html)
- W1. [Introduction: Analysis and Comprehension of High Throughput Genomic Data](W1-Introduction.html)
- W2. [Sequences, Alignments, and Large Data](W3-Large-Data.html)
- W3. [RNA-Seq Known-gene Differential Expression](W2-RNASeq.html)
- W4. [Gene, Genome, and Variant Annotation](W4-Annotation.html)
- W5. (Extra) [Shiny for Interactive Visualization](W5-Shiny.html)

# Acknowledgments and Resources

## Acknowledgements

- Core (Seattle / Buffalo): Sonali Arora, Brian Long, Marc Carlson,
  Nate Hayden, Jim Hester, Jim Java, Valerie Obenchain, Herv&eacute;
  Pag&egrave;s, Paul Shannon, Dan Tenenbaum.

- The research reported in this presentation was supported by the
  National Cancer Institute and the National Human Genome Research
  Institute of the National Institutes of Health under Award numbers
  U24CA180996 and U41HG004059, and the National Science Foundation
  under Award number 1247813. The content is solely the responsibility
  of the authors and does not necessarily represent the official views
  of the National Institutes of Health or the National Science
  Foundation.

## Key references

- Irizarry R, et al. (2015) <a
  href="http://genomicsclass.github.io/book/">Biomedical Data
  Science</a>. Course Notes, EdX PH525.1x.
- Huber W, et al. (2015) <a
  href="http://www.nature.com/nmeth/journal/v12/n2/abs/nmeth.3252.html">Orchestrating
  high-throughput genomic analysis with
  <em>Bioconductor</em></a>. Nature Methods 12:115-121;
  doi:10.1038/nmeth.3252 (full-text free with registration).
- Lawrence M, Huber W, Pag&egraves;s H, Aboyoun P, Carlson M, et al. (2013) <a
  href="http://dx.doi.org/10.1371/journal.pcbi.1003118">Software for
  Computing and Annotating Genomic Ranges</a>. PLoS Comput Biol 9(8):
  e1003118. doi: 10.1371/journal.pcbi.1003118
